Toadflax Analysis

### 2024-03-07 toadflax_report.qmd
commit

<div style="border: 3px solid #427EDC; padding: 10px; ">
After running all of these plots, it looks to me like the largest differences are between the PRE and Post PCA Model plots when we removed the Natural category. Looking at the hybrid comparison, it looks like the plots are basically the same, just flipped on an axis or two. 
</div>

>>>>

<div style="border: 1px solid black; padding: 10px; ">
After running all of these plots, it looks to me like the largest differences are between the PRE and Post PCA Model plots when we removed the Natural category. Looking at the hybrid comparison, it looks like the plots are basically the same, just flipped on an axis or two. 
</div>
